Age-related changes in plant growth and traits

### 2015-09-08 leaf_weight_issue.Rmd
trying to understand problem with leaf weight estimates

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=15, fig.height=15}
par(mfcol=c(2,2), cex=1, omi=c(.3,.2,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
data2 <- subset(HarvestData,start_end=="end")
data2 <- split(data2, data2$species)

data1 <- subset(HarvestData,start_end=="end"&age>8)
data1 <- split(data1, data1$species)

for(spp in names(data)) {

plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)

plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)

}
```

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=15, fig.height=15}
par(mfcol=c(2,2), cex=1, omi=c(.3,.2,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
xvar <- "diameter"
yvar <- "leaf_weight"

data2 <- subset(HarvestData, start_end=="end"&segment==1 & !is.na(diameter) )
data2 <- split(data2, data2$species)

for(spp in names(data2)) {
data3 <- data2[[spp]]
x <- data3[[xvar]]
plot(leaf_weight~diameter,data3,log="xy",pch=16,col=col.age(data2[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data3,segment==1),cex=1.5)
fit <- lm(log(data3[[yvar]]) ~  log(x))
cs <- coef(fit)
slope <- cs[2]
curve(exp(cs[1])*x^slope, from=0.1, to=100, add=TRUE, lwd=2)
intercept_indiv = log(data3[[yvar]]) - slope * log(x)

for(i in seq_len(nrow(data3))) {
  curve(exp(intercept_indiv[i])*x^slope, from= 0.9*x[i], to=1.1*x[i], add=TRUE, lwd=1)
  }

}

#plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data1[[spp]]$age),main=spp,cex=1.2)
#points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)

```
